---
title: "Solar-Demand_Energy_Forecasting"
author: "Mahdi Abolghasemi"
date: "23/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=6)

# Load packages
library(tidyverse)
library(scales)
library(lubridate)
library(tsibble)
library(cowplot)
library(visdat)
library(naniar)
library(viridis)
library(ggExtra)
library(mgcv)
library(naniar)
library(visdat)
library(plotly)
library(purrr)
library(chron)
library(ggrepel)
library(reshape2)
library(forecast)
library(ggthemes)
library(scales)
library(gridExtra)
library(grid)
library(fable)
library(openair)
library(ggmap)
library(lemon)
library(formattable)
library(Hmisc)
library(corrplot)
#library(ggcorrplot)
library(lattice)
library(knitr)
library(kableExtra)
library(feasts)
library(furrr)
library(sugrrants)
library(tidymodels)
library(here)
library(lightgbm)
library(oce)
library(openair)

# deactivate scientific notation
options(scipen = 999)

# Set plot theme
theme_set(theme_bw())
```

# Reading data


# Preprocessing data and creating some calendar features
I save the calendar features in data frames and save it in the following objects, so we can use it from here on.
```{r, echo=FALSE}
#saveRDS(tsibble_data_Oct, "tsibble_data_Oct.rds")
tsibble_data_Oct <- read_rds(here::here("Data","tsibble_data_Oct.rds"))

#saveRDS(tsibble_data_All, "tsibble_data_All_UTC.rds")
tsibble_data_All <- read_rds(here::here("Data", "tsibble_data_All_UTC.rds"))
```

There is an outlier in October data, we replace it with na. 
```{r}
tsibble_data_Oct <- tsibble_data_Oct %>% replace_with_na(list(series_value=1744.1))
```

# Check for outliers, negative, missing values

We can see that there are lots of missing values across both solars and buildings data. We remove them from our series. 


```{r}
#defining solars and buildings 
solars <- c("Solar0", "Solar1", "Solar2", "Solar3", "Solar4", "Solar5")
buildings <- c("Building0", "Building1", "Building3", "Building4", "Building5", "Building6")
```

```{r fig.height=9, fig.width=16, eval=FALSE}
# Vector of each month in the  data
Months <- tsibble_data_All %>% distinct(Month) %>% pull()
```

Descriptive statistics of data is shown below.
```{r desc_stat-table, echo=FALSE, eval=TRUE}
tsibble_data_All %>% na.omit() %>% 
  select(series_name, Date, Year, Month, Day_of_Month, Day, Week, Hour, Minute, series_value) %>%
  group_by(series_name) %>%
  summarise(mean_series_value_avg = round(mean(series_value, na.rm=TRUE), 2),
            sd_series_value_avg = round(sd(series_value), 2),
            iqr_series_value_avg = IQR(series_value),
            min_series_value_avg = min(series_value),
            max_series_value_avg = max(series_value)) %>%
  ungroup() %>%
  kable("html", booktabs = T, col.names = c("Groups", "Mean", "Std. Dev.", "IQR", "Min", "Max"), caption = "Summary statistics of Avg. Power and Demand in Different Groups.") %>%
  kable_styling(latex_options = c("hold_position"), position = "center") %>%
  column_spec(1, bold=F) %>%
  kableExtra::collapse_rows(columns = 1, latex_hline = "major", valign = "middle")
```

There are many periods that solar power is not generated. Most of them obviously are during evenings/nights/early mornings but also sometimes before noon which may be impacted by weather conditions, e.g, cloud coverage.  

```{r fig_period_no_solarpower, echo=FALSE}
#periods without solar power during the hours of day
tsibble_data_All %>%
  filter(series_name %in% solars) %>%
  filter(series_value == 0) %>%
  group_by(Hour) %>%
  mutate(fifteen_minute_instances = n()) %>%
  ungroup() %>%
  #mutate(Duration = (fifteen_minute_instances/4)/24) %>%
  ggplot(aes(x = Hour, y = fifteen_minute_instances)) +
  geom_bar(stat = "identity") +
  facet_wrap(~Month) +
  labs(subtitle = "Number of Periods without solar power",
           y = "Total Number of periods without solar power (15mins periods)",
           x = "Hour of the day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_continuous(breaks= scales::pretty_breaks(n = 24), expand = c(0,0))
```

We further look in to each panel to see which ones generate zero power more often. It seems like they all have similar distribution except solar 0 which is just lower. We may be able to build a unique model for all of them. 
```{r fig_period_no_solarpower, echo=FALSE}
#periods without solar power during the hours of day
tsibble_data_All %>%
  filter(series_name %in% solars) %>%
  filter(series_value == 0) %>%
  group_by(Hour) %>%
  mutate(fifteen_minute_instances = n()) %>%
  ungroup() %>%
  mutate(Duration = (fifteen_minute_instances/4)/24) %>%
  ggplot(aes(x = Hour, y = fifteen_minute_instances)) +
  geom_bar(stat = "identity") +
  facet_wrap(~series_name) +
  labs(subtitle = "Number of Periods without solar power",
           y = "Total periods without solar power (number of 15 mins)",
           x = "Hour of the day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_continuous(breaks= scales::pretty_breaks(n = 24), expand = c(0,0))
```

Solar power has a nice normal distribution as shown below. More powers in midday and less over other periods. 

```{r fig_period_avg_solarpower, echo=FALSE}
tsibble_data_All %>%
  filter(series_name %in% solars) %>%
  filter(series_value >= 0) %>%
  group_by(Hour) %>%
  mutate(mean_power = mean(series_value, na.rm = TRUE))%>%
  ungroup() %>%
  #mutate(Duration = (fifteen_minute_instances/4)/24) %>%
  ggplot(aes(x = Hour, y = mean_power)) +
  geom_bar(stat = "identity") +
  facet_wrap(~series_name) +
  labs(subtitle = "Avg Solar Power over the day for each solar panel",
           y = "Avg solar power (Kw)",
           x = "Hour of the day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_continuous(breaks= scales::pretty_breaks(n = 24), expand = c(0,0))
```

## Exploratory data analysis for buildings

There is no period with negative or zero demand for buildings. Only positive ones as shown below. The largest demand is between 7 AM- 10 pm. 
It is interesting that except building 5 , the rest of require a significant amount of energy which may be indicative of bigger building, or more scheduled classes during those times. 

```{r period_no_demand, echo=FALSE}
# Plot of total hours without power production in each month
tsibble_data_All %>%
  filter(series_name %in% buildings) %>%
  filter(series_value == 0)
```
The grpah below shows the average power required in buildings over the years.
```{r fig_period_avg_demand_hour, echo=FALSE}
tsibble_data_All %>%
  filter(series_name %in% buildings) %>%
  filter(series_value >= 0) %>%
  group_by(Hour, Year) %>%
  mutate(mean_power = mean(series_value)) %>%
  ungroup() %>%
  #mutate(Duration = (fifteen_minute_instances/4)/24) %>%
  ggplot(aes(x = Hour, y = mean_power/1000)) +
  geom_bar(stat = "identity") +
  facet_wrap(Year~series_name) +
  labs(subtitle = "Avg Demand over Periods",
           y = "Demand",
           x = "Hour of the day") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_continuous(breaks= scales::pretty_breaks(n = 24), expand = c(0,0))
```


We looked into the power over each month and day of the week. There is less power required over the weekends, i.e, days 6 and 7. We can see that there is more power required during March which may attribute to the start of semester at Monash University. 
```{r fig_period_avg_demand_day,  fig.height=10, echo=FALSE}
tsibble_data_All %>%
  filter(series_name %in% buildings) %>%
  filter(series_value >= 0) %>%
  group_by(Day, Month, Year) %>%
  mutate(mean_power = mean(series_value)) %>%
  ungroup() %>%
  #mutate(Duration = (fifteen_minute_instances/4)/24) %>%
  ggplot(aes(x = (Day), y = mean_power)) +
  geom_bar(stat = "identity") +
  facet_wrap(Year ~ Month) +
  labs(subtitle = "Avg Demand over Days",
           y = "Demand",
           x = "Day of the Month") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_continuous(breaks= scales::pretty_breaks(n = 7), expand = c(0,0))
```



# Wrangling weather data

We downloaded solar, rain fall, max and min temperature from BOM. These data sets are recorded for each day which may not be ideal for our forecasting as we generate forecast for each 15 minute time slot. There is minutely data available that can be purchased but we continue with the daily data. 

```{r}
# this is the recorded data as done above.
#saveRDS(Weather_data, "Weather_data.rds")
Weather_data <- read_rds(here::here("Data", "Weather_data.rds"))
```


```{r fig_avr_exposure, message=FALSE , echo=FALSE, fig.width=10, fig.height=7.5, fig.pos="H"}
# Time plot of avg temperature grouped by Time
Weather_data %>%
  group_by(Day, Month) %>%
  summarise(mean_Expo_avg = mean(Avg_Exposure)) %>%
  ungroup() %>%
  ggplot(aes(x = as.factor(Day), y = mean_Expo_avg)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ Month) +
  #scale_color_manual(values=group.colours, breaks = c("Summer", "Autumn", "Winter", "Spring")) +
  scale_colour_brewer(palette = "Set1") +
  labs(title =  "Mean of Exposure during the year",
       y = "Me an of Exposure (Megajuoules/Square meter)",
       x = "Day") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  #theme(legend.position="bottom") +
  guides(colour = guide_legend(override.aes = list(size = 1.5, alpha = 1)))
```

```{r fig_avr_rain, message=FALSE , echo=FALSE, fig.width=10, fig.height=7.5, fig.pos="H"}
# Time plot of avg rainfall grouped by Time
Weather_data %>%
  group_by(Day, Month) %>%
  summarise(mean_RainFall_avg = mean(Avg_RainFall)) %>%
  ungroup() %>%
  ggplot(aes(x = as.factor(Day), y = mean_RainFall_avg)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ Month) +
  scale_colour_brewer(palette = "Set1") +
  labs(title =  "Mean of RainFall during the year",
       y = "Mean of RainFall",
       x = "Day") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  guides(colour = guide_legend(override.aes = list(size = 1.5, alpha = 1)))
```


```{r fig_avr_maxtemp, message=FALSE , echo=FALSE, fig.width=10, fig.height=7.5, fig.pos="H"}
# Time plot of avg max temp grouped by Time
Weather_data %>%
  group_by(Day, Month) %>%
  summarise(mean_MaxTemp_avg = mean(Avg_MaxTemp)) %>%
  ungroup() %>%
  ggplot(aes(x = as.factor(Day), y = mean_MaxTemp_avg)) +
  geom_bar(stat = "identity") +
  facet_wrap( ~ Month) +
  scale_colour_brewer(palette = "Set1") +
  labs(title =  "Mean of Max Temp during the year",
       y = "Mean of Max Temp",
       x = "Day") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 5, angle = 45, hjust = 1)) +
  guides(colour = guide_legend(override.aes = list(size = 1.5, alpha = 1)))
```


Creating solar and building data
```{r, echo=FALSE}
tsibble_data_solar <- tsibble_data_All %>%
  filter(series_name %in% solars)
```

```{r , echo=FALSE}
tsibble_data_building <- tsibble_data_All %>%
  filter(series_name %in% buildings)
```

We run preprocessing on building and solar data to clean up the missing values, choose the relavant observations, and save the final. The final data are saved below. 

```{r}
# saveRDS(tsibble_data_clean, "tsibble_data_clean.rds")
# saveRDS(solar_clean_all, "solar_clean_all.rds")
# saveRDS(building_clean_all, "building_clean_all.rds")
tsibble_data_clean <- read_rds(here::here("Data","tsibble_data_clean.rds"))
solar_clean_all <- read_rds(here::here("Data", "solar_clean_all.rds"))
building_clean_all <- read_rds(here::here("Data","building_clean_all.rds"))
building_clean_all <- building_clean_all %>% replace_with_na(list(series_value=1744.1))
```


## Feature Engineering daily weather data: BOM data

We create some rolling features for weather data. This will be used later in the forecasting model. 
```{r}
Daily_WeatherData_Feats <- Weather_data %>%
  mutate(max_Temp_rollingMean_2_day = zoo::rollapply(Avg_MaxTemp, width = 2, FUN = mean, align = "right", fill = NA),
         max_Temp_rollingSd_3_day = zoo::rollapply(Avg_MaxTemp, width = 3, FUN = sd, align = "right", fill = NA),
         
         min_Temp_rollingMean_2_day = zoo::rollapply(Avg_MinTemp, width = 2, FUN = mean, align = "right", fill = NA),
         min_Temp_rollingSd_3_day = zoo::rollapply(Avg_MinTemp, width = 3, FUN = sd, align = "right", fill = NA),
         
         SolarExpo_rollingMean_2_day = zoo::rollapply(Avg_Exposure, width = 2, FUN = mean, align = "right", fill = NA),
         SolarExpo_rollingSd_3_day = zoo::rollapply(Avg_Exposure, width = 3, FUN = sd, align = "right", fill = NA),
         
         RainFall_rollingMean_2_day = zoo::rollapply(Avg_RainFall, width = 2, FUN = mean, align = "right", fill = NA),
         RainFall_rollingSd_3_day = zoo:: rollapply(Avg_RainFall, width = 3, FUN = sd, align = "right", fill = NA))

lags <- 1:3
lag_names <- paste("lag", formatC(lags, width = nchar(max(lags)), flag = "0"), 
  sep = "_")
lag_functions <- setNames(paste("dplyr::lag(., ", lags, ")"), lag_names)

# Create lags of series values
Daily_WeatherData_Feats <- Daily_WeatherData_Feats %>%
  mutate_at(vars(Avg_MaxTemp ,Avg_MinTemp, Avg_RainFall, Avg_Exposure), funs_(lag_functions)) %>%
  rename_at(vars(starts_with("lag")), ~ paste0("lag_",.x))
```

```{r}
#saveRDS(Daily_WeatherData_Feats, "Daily_WeatherData_Feats.rds")
Daily_WeatherData_Feats <- read_rds(here::here("Data","Daily_WeatherData_Feats.rds"))
```

## Feature engineering hourly weather data: ERA data

```{r}
ERA_Feats <- ERA %>% 
  mutate(Hour= hour(TimeDate), Date= date(TimeDate)) %>%
  mutate(Temperature_rollingMean_3_hours = zoo::rollapply(Temperature, width = 3, FUN = mean, align = "right", fill = NA),
         Temperature_rollingMean_6_hours = zoo::rollapply(Temperature, width = 6, FUN = mean, align = "right", fill = NA),
         Temperature_rollingSd_6_hours = zoo::rollapply(Temperature, width = 6, FUN = sd, align = "right", fill = NA),
         
         TemperatureDew_rollingMean_3_hours = zoo::rollapply(TemperatureDew, width = 3, FUN = mean, align = "right", fill = NA),
         TemperatureDew_rollingMean_6_hours = zoo::rollapply(TemperatureDew, width = 6, FUN = mean, align = "right", fill = NA),
         TemperatureDew_rollingSd_6_hours = zoo::rollapply(TemperatureDew, width = 6, FUN = sd, align = "right", fill = NA),
         
         WindSpeed_rollingMean_3_hours = zoo::rollapply(WindSpeed, width = 3, FUN = mean, align = "right", fill = NA),
         WindSpeed_rollingMean_6_hours = zoo::rollapply(WindSpeed, width = 6, FUN = mean, align = "right", fill = NA),
         WindSpeed_rollingSd_6_hours = zoo::rollapply(WindSpeed, width = 6, FUN = sd, align = "right", fill = NA),
                  
         Pressure_rollingMean_3_hours = zoo::rollapply(Pressure, width = 3, FUN = mean, align = "right", fill = NA),
         Pressure_rollingMean_6_hours = zoo::rollapply(Pressure, width = 6, FUN = mean, align = "right", fill = NA),
         Pressure_rollingSd_6_hours = zoo::rollapply(Pressure, width = 6, FUN = sd, align = "right", fill = NA),
         
         Humidity_rollingMean_3_hours = zoo::rollapply(Humidity, width = 3, FUN = mean, align = "right", fill = NA),
         Humidity_rollingMean_6_hours = zoo::rollapply(Humidity, width = 6, FUN = mean, align = "right", fill = NA),
         Humidity_rollingSd_6_hours = zoo::rollapply(Humidity, width = 6, FUN = sd, align = "right", fill = NA),
         
         Solar_radiation_rollingMean_3_hours = zoo::rollapply(Surface_solar_radiation, width=3, FUN = mean,align="right", fill = NA),
         Solar_radiation_rollingMean_6_hours = zoo::rollapply(Surface_solar_radiation, width = 6, FUN=mean,align="right", fill = NA),
         Solar_radiation_rollingSd_6_hours = zoo::rollapply(Surface_solar_radiation, width = 6,FUN=sd,align="right",fill = NA),
         
         Thermal_radiation_rollingMean_3_hours=zoo::rollapply(Surface_Thermal_radiation,width=3,FUN=mean,align = "right", fill = NA),
         Thermal_radiation_rollingMean_6_hours=zoo::rollapply(Surface_Thermal_radiation,width=6,FUN=mean,align = "right", fill = NA),
         Thermal_radiation_rollingSd_6_hours=zoo::rollapply(Surface_Thermal_radiation,width=6,FUN=sd,align = "right", fill = NA),
         
         Cloud_Cove_rollingMean_3_hours = zoo::rollapply(Cloud_Cove, width = 3, FUN = mean, align = "right", fill = NA),
         Cloud_Cove_rollingMean_6_hours = zoo::rollapply(Cloud_Cove, width = 6, FUN = mean, align = "right", fill = NA),
         Cloud_Cove_rollingSd_6_hours = zoo::rollapply(Cloud_Cove, width = 6, FUN = sd, align = "right", fill = NA))

lags <- 1:3
lag_names <- paste("lag", formatC(lags, width = nchar(max(lags)), flag = "0"), 
  sep = "_")
lag_functions <- setNames(paste("dplyr::lag(., ", lags, ")"), lag_names)

# Create lags of series values
ERA_Feats <- ERA_Feats %>%
  mutate_at(vars(Temperature,TemperatureDew,Surface_solar_radiation,Humidity,Pressure,Surface_Thermal_radiation, Cloud_Cove), funs_(lag_functions)) %>%
  rename_at(vars(starts_with("lag")), ~ paste0("lag_",.x))
```


```{r}
#saveRDS(ERA_Feats,here("Data", "ERA_Feats.RDS"))
ERA_Feats <- read_rds(here::here("Data", "ERA_Feats.rds"))
```

## Creating required data for buildings and solar: daily data
```{r train-data_building, eval=TRUE}
 building_clean_weather_daily <- building_clean_all %>% 
  left_join(Daily_WeatherData_Feats %>% select(-Day, -Year, -Month, -(contains("lag"))), by= c("Date"="index"))

building_clean_weather_train_daily <- building_clean_weather_daily %>%
    filter(Date < "2020-11-01") %>%
    select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
   select(-start_timestamp,-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day)

building_clean_weather_test_daily <- building_clean_weather_daily %>%
  filter((Date) >= "2020-09-01" & Date < "2020-11-01") %>% 
  distinct(TimeDate,series_name, .keep_all = TRUE) %>%
select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
   select(-start_timestamp,-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day)
```


```{r train-data_solars, eval=TRUE}
 solar_clean_weather_daily <- solar_clean_all %>% 
  left_join(Daily_WeatherData_Feats %>% select(-Day, -Year, -Month, -(contains("lag"))), by= c("Date"="index"))

solar_clean_weather_train_daily <- solar_clean_weather_daily %>%
    filter(Date < "2020-11-01") %>%
    select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
    select(-start_timestamp,-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)

solar_clean_weather_test_daily <- solar_clean_weather_daily %>%
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
  distinct(TimeDate,series_name, .keep_all = TRUE) %>%
   select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
  select(-start_timestamp,-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)
```


```{r}
Daily_WeatherData_Feats_Oct_building <- Daily_WeatherData_Feats %>% 
   select(-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day) %>%
  select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-10-01" & index <"2020-11-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 31*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```

```{r}
Daily_WeatherData_Feats_Oct_solar <- Daily_WeatherData_Feats %>%  
    select(-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day) %>%
   select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-10-01" & index <"2020-11-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 31*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```

```{r}
Daily_WeatherData_Feats_Nov_building <- Daily_WeatherData_Feats %>% 
   select(-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day) %>%
  select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-11-01" & index <"2020-12-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 30),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```

```{r}
Daily_WeatherData_Feats_Nov_solar <- Daily_WeatherData_Feats %>%  
  ##### NOTe    IMPORTANT### This is only needed for dailyhourly, for daily it must be deactivated
    #select(-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day) %>% 
   select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-11-01" & index <"2020-12-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 30),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```

## Models and Predictions with daily data

```{r}
lgbm_mod_b0_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01") %>% #use this data for October/November
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Building0") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
    filter(series_name=="Building0") %>% pull(series_value),
  num_leaves = 20L, 
  max_depth = 10, 
  learning_rate = 0.1,  
  nrounds = 80,  
  #feature_fraction = 0.8, # not useful
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_b1_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix( building_clean_weather_train_daily %>% filter(series_name=="Building1") %>%
                      as_tibble()  %>% 
                      filter(Date < "2020-11-01") %>% select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily %>% filter(series_name=="Building1")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100,
  max_depth = 9,
  learning_rate = 0.1,
  nrounds = 120,
  #max_bin = 550L,
  min_data_in_leaf = 120,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_b3_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01")%>% 
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Building3") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>% 
    filter(series_name=="Building3") %>% pull(series_value),
  num_leaves = 20L,  
  max_depth = 10,  
  learning_rate = 0.1,  
  nrounds = 120,  
  #feature_fraction = 0.7, 
  min_data_in_leaf = 80,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)

lgbm_mod_b4_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily %>% filter(series_name=="Building4")  %>% 
                     filter( Date < "2020-11-01") %>%
                     as_tibble() %>% select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily %>% filter(series_name=="Building4")  %>% 
    filter(Date < "2020-11-01")%>% pull(series_value),
  num_leaves = 80L, 
  max_depth = 7,  
  learning_rate = 0.1,  
  nrounds = 30L, 
  #feature_fraction = 0.7,  
  min_data_in_leaf = 300,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_b5_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date < "2020-11-01") %>% #Date>"2020-01-01" & 
                     filter(series_name=="Building5") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)), #%>%
   # mutate(End_lock_down= case_when(
     # Date>="2020-10-19" ~ 1,
     # Date<"2020-10-19" ~ 0))),
  label = building_clean_weather_train_daily   %>% 
    filter(Date < "2020-11-01") %>% #Date>"2020-01-01" & 
    filter(series_name=="Building5") %>% pull(series_value),
  num_leaves = 52, #200L,  
  max_depth = 8,  
  learning_rate = 0.1, #0.1,   
  nrounds = 25L,  
  #feature_fraction = 0.7,
  min_data_in_leaf = 50, #180,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)



lgbm_mod_b6_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date>"2020-01-01" & Date < "2020-11-01") %>% 
                     filter(series_name=="Building6") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-01-01" & Date < "2020-11-01") %>%
    filter(series_name=="Building6") %>% pull(series_value),
  num_leaves = 30L,  
  max_depth = 7, 
  learning_rate = 0.1,  
  nrounds = 30L, 
  #feature_fraction = 1,  
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",
  lambda_l1 = 0.1, 
  verbose = -1)

# One-month LightGBM mod
lgbm_mod_s0_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar0")  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-contains("rolling"))%>%
                     as_tibble() %>% select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
    select(-contains("rolling"))%>%
    filter(series_name=="Solar0") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L, 
  max_depth = 9,
  learning_rate = 0.1,
  nrounds = 100L,
  #max_bin = 550L,# not useful 
  #feature_fraction = 0.8, # not useful
  min_data_in_leaf = 50,
  objective = "mae",
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = .1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_s1_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar1") %>%
                     as_tibble()%>% 
                     filter(Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar1")  %>% 
    filter( Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,  
  max_depth = 8,  
  learning_rate = 0.1, 
  nrounds = 85L,
  #feature_fraction = 0.7,  
  min_data_in_leaf = 250, 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s2_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar2") %>%
                     as_tibble()  %>% 
                     filter( Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar2")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,  
  max_depth = 7,  
  learning_rate = 0.1,  
  nrounds = 80L, 
 # feature_fraction = 0.7,  
  min_data_in_leaf = 50,   
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.2,  
  verbose = -1)


lgbm_mod_s3_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01")%>% 
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Solar3") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01")%>%
    filter(series_name=="Solar3") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L, 
  max_depth = 7, 
  learning_rate = 0.1, 
  nrounds = 70L,  
 # feature_fraction = 0.7,  
  min_data_in_leaf = 50,  
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)


lgbm_mod_s4_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar4") %>%
                     as_tibble()  %>% 
                     filter(Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar4")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 180L, 
  max_depth = 12, 
  learning_rate = 0.1,  
  nrounds = 40L,  
  #feature_fraction = 0.7,  
  min_data_in_leaf = 50, # 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)

lgbm_mod_s5_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar5") %>%
                     as_tibble()  %>% 
                     filter( Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar5")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 80L,  
  max_depth = 10,  
  learning_rate = 0.1, 
  nrounds = 37, 
  #feature_fraction = 0.7,  
  min_data_in_leaf = 300, 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)
```


```{r}
predict_lgbm_b0_f1mae_daily <- predict(lgbm_mod_b0_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))
predict_lgbm_b1_f1mae_daily <- predict(lgbm_mod_b1_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))
predict_lgbm_b3_f1mae_daily <- predict(lgbm_mod_b3_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))
predict_lgbm_b4_f1mae_daily <- predict(lgbm_mod_b4_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))
predict_lgbm_b5_f1mae_daily <- predict(lgbm_mod_b5_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))
predict_lgbm_b6_f1mae_daily <- predict(lgbm_mod_b6_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b_f1mae_daily <- rbind(predict_lgbm_b0_f1mae_daily, predict_lgbm_b1_f1mae_daily, predict_lgbm_b3_f1mae_daily, predict_lgbm_b4_f1mae_daily, predict_lgbm_b5_f1mae_daily, predict_lgbm_b6_f1mae_daily)

# Solar forecast October
predict_lgbm_s0_f1mae_daily <- predict(lgbm_mod_s0_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar %>% select(-contains("rolling"))))
predict_lgbm_s1_f1mae_daily <- predict(lgbm_mod_s1_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))
predict_lgbm_s2_f1mae_daily <- predict(lgbm_mod_s2_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))
predict_lgbm_s3_f1mae_daily <- predict(lgbm_mod_s3_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))
predict_lgbm_s4_f1mae_daily <- predict(lgbm_mod_s4_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))
predict_lgbm_s5_f1mae_daily <- predict(lgbm_mod_s5_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s_f1mae_daily <- rbind(predict_lgbm_s0_f1mae_daily, predict_lgbm_s1_f1mae_daily, predict_lgbm_s2_f1mae_daily, predict_lgbm_s3_f1mae_daily, predict_lgbm_s4_f1mae_daily, predict_lgbm_s5_f1mae_daily)

# turn small values to zero
predict_lgbm_s_f1mae_daily[predict_lgbm_s_f1mae_daily<0.15]=0
predict_lgbm_b_f1mae_daily[predict_lgbm_b_f1mae_daily<0.01]=0
```

```{r}
predict_lgbm_b0_f1mae_daily <- predict(lgbm_mod_b0_f1mae_daily, as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building0") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b1_f1mae_daily <- predict(lgbm_mod_b1_f1mae_daily,as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building1") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b3_f1mae_daily <- predict(lgbm_mod_b3_f1mae_daily, as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building3") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b4_f1mae_daily <- predict(lgbm_mod_b4_f1mae_daily, as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building4") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b5_f1mae_daily <- predict(lgbm_mod_b5_f1mae_daily, as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building5") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b6_f1mae_daily <- predict(lgbm_mod_b6_f1mae_daily, as.matrix(building_clean_weather_test_daily %>% filter(series_name=="Building6") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_b_f1mae_daily <- rbind(predict_lgbm_b0_f1mae_daily, predict_lgbm_b1_f1mae_daily, predict_lgbm_b3_f1mae_daily, predict_lgbm_b4_f1mae_daily, predict_lgbm_b5_f1mae_daily, predict_lgbm_b6_f1mae_daily)

# Solar forecast October
predict_lgbm_s0_f1mae_daily <- predict(lgbm_mod_s0_f1mae_daily, as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar0") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate) %>% select(-contains("rolling"))))

predict_lgbm_s1_f1mae_daily <- predict(lgbm_mod_s1_f1mae_daily, as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar1") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_s2_f1mae_daily <- predict(lgbm_mod_s2_f1mae_daily,as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar2") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_s3_f1mae_daily <- predict(lgbm_mod_s3_f1mae_daily, as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar3") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_s4_f1mae_daily <- predict(lgbm_mod_s4_f1mae_daily, as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar4") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_s5_f1mae_daily <- predict(lgbm_mod_s5_f1mae_daily, as.matrix(solar_clean_weather_test_daily %>% filter(series_name=="Solar5") %>% as_tibble() %>% select(-series_value, -series_name, -TimeDate)))

predict_lgbm_s_f1mae_daily <- rbind(predict_lgbm_s0_f1mae_daily, predict_lgbm_s1_f1mae_daily, predict_lgbm_s2_f1mae_daily, predict_lgbm_s3_f1mae_daily, predict_lgbm_s4_f1mae_daily, predict_lgbm_s5_f1mae_daily)

# turn small values to zero
predict_lgbm_s_f1mae_daily[predict_lgbm_s_f1mae_daily<0.1]=0
```

```{r}
predict_sb_daily <- rbind(predict_lgbm_b_f1mae_daily,predict_lgbm_s_f1mae_daily)
rownames(predict_sb_daily) <- c(buildings, solars)
write.csv(predict_sb_daily, "i2d-Nov.csv")
```


```{r}
# lightgbm::lgb.save(lgbm_mod_b0_f1mae_daily, "lgbm_mod_b0_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_b1_f1mae_daily, "lgbm_mod_b1_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_b3_f1mae_daily, "lgbm_mod_b3_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_b4_f1mae_daily, "lgbm_mod_b4_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_b5_f1mae_daily, "lgbm_mod_b5_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_b6_f1mae_daily, "lgbm_mod_b6_f1mae_daily_nov.txt")
# 
# lightgbm::lgb.save(lgbm_mod_s0_f1mae_daily, "lgbm_mod_s0_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_s1_f1mae_daily, "lgbm_mod_s1_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_s2_f1mae_daily, "lgbm_mod_s2_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_s3_f1mae_daily, "lgbm_mod_s3_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_s4_f1mae_daily, "lgbm_mod_s4_f1mae_daily_nov.txt")
# lightgbm::lgb.save(lgbm_mod_s5_f1mae_daily, "lgbm_mod_s5_f1mae_daily_nov.txt")

lgbm_mod_b0_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b0_f1mae_daily_oct.txt"))
lgbm_mod_b1_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b1_f1mae_daily_oct.txt"))
lgbm_mod_b3_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b3_f1mae_daily_oct.txt"))
lgbm_mod_b4_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b4_f1mae_daily_oct.txt"))
lgbm_mod_b5_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b5_f1mae_daily_oct.txt"))
lgbm_mod_b6_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b6_f1mae_daily_oct.txt"))

lgbm_mod_s0_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s0_f1mae_daily_oct.txt"))
lgbm_mod_s1_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s1_f1mae_daily_oct.txt"))
lgbm_mod_s2_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s2_f1mae_daily_oct.txt"))
lgbm_mod_s3_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s3_f1mae_daily_oct.txt"))
lgbm_mod_s4_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s4_f1mae_daily_oct.txt"))
lgbm_mod_s5_f1mae_daily <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s5_f1mae_daily_oct.txt"))
```

### Variable importance buildings and solars daily
```{r eval=FALSE}
# Feature importance
lgbm_ImpVar_b0_daily <- lightgbm::lgb.importance(lgbm_mod_b0_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_b1_daily <- lightgbm::lgb.importance(lgbm_mod_b1_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_b3_daily <- lightgbm::lgb.importance(lgbm_mod_b3_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_b4_daily <- lightgbm::lgb.importance(lgbm_mod_b4_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_b5_daily <- lightgbm::lgb.importance(lgbm_mod_b5_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_b6_daily <- lightgbm::lgb.importance(lgbm_mod_b6_f1mae_daily, percentage = TRUE)

# Save feature importance
# saveRDS(lgbm_ImpVar_b0,  ("lgbm_ImpVar_b0.rds"))
# saveRDS(lgbm_ImpVar_b1,  ("lgbm_ImpVar_b1.rds"))
# saveRDS(lgbm_ImpVar_b3,  ("lgbm_ImpVar_b3.rds"))
# saveRDS(lgbm_ImpVar_b4,  ("lgbm_ImpVar_b4.rds"))
# saveRDS(lgbm_ImpVar_b5,  ("lgbm_ImpVar_b5.rds"))
# saveRDS(lgbm_ImpVar_b6,  ("lgbm_ImpVar_b6.rds"))

lgbm_ImpVar_s0_daily <- lightgbm::lgb.importance(lgbm_mod_s0_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_s1_daily <- lightgbm::lgb.importance(lgbm_mod_s1_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_s2_daily <- lightgbm::lgb.importance(lgbm_mod_s2_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_s3_daily <- lightgbm::lgb.importance(lgbm_mod_s3_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_s4_daily <- lightgbm::lgb.importance(lgbm_mod_s4_f1mae_daily, percentage = TRUE)
lgbm_ImpVar_s5_daily <- lightgbm::lgb.importance(lgbm_mod_s5_f1mae_daily, percentage = TRUE)

# View feature importance rank
# lgbmSpotMod_ImpVar %>% View
lgbm_ImpVar_s0_daily %>%
  as_tibble() %>%
  ggplot(aes(x = fct_reorder(Feature, Gain), y = Gain)) +
  geom_col(alpha = 0.8) +
  labs(title = "Feature importances ranking",
       x = "Features") +
  coord_flip() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.border = element_blank(),
  axis.line = element_line())
```


# post analysing daily dta

```{r}

predict_sb_daily %>% t() %>% as_tibble()  %>% 
  pivot_longer(cols= c(1:12),names_to = "series_name", values_to= "Forecast") %>%
  #arrange("Names", desc())  %>%
  mutate(h= rep((1:2976), each=12)) %>% 
left_join(tsibble_data_Oct  %>% as_tibble() %>%  select(TimeDate,series_value,series_name) %>% mutate(h= rep(c(1:2976), 12))) %>%
  pivot_longer(cols = c(series_value, Forecast), names_to = "Type", values_to = "Power") %>%
  filter(series_name == "Building5") %>%
  ggplot(aes(x = TimeDate, y = Power, colour = Type)) +
  geom_line() +
  labs(title = "Forecast vs. Actual",
       colour = NULL) +
  #facet_wrap(~ series_name, scales = "free", ncol = 3) +
  #scale_x_datetime(breaks = "1 hours", labels = date_format("%H:%M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        legend.position = "bottom")
```


#### Creating data with ERA for hourly data ####


```{r}
building_clean_weather_train_hourly <- building_clean_all %>% 
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,series_name, -TimeDate, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(Date, Hour, contains("Temperature"), -contains("Dew")), by= c("Date", "Hour")) 

building_clean_weather_test_hourly <- building_clean_all %>% 
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
  distinct(TimeDate, series_name, .keep_all = TRUE) %>%
  select(-start_timestamp,series_name, -TimeDate, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(Date, Hour, contains("Temperature"), -contains("Dew")), by= c("Date", "Hour")) %>%
  replace_with_na(list(series_value=1744.1)) ## this is the big outlier in
 

solar_clean_weather_train_hourly <- solar_clean_all %>%
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats, by= c("Date", "Hour")) #%>% select(-TimeDate, -contains(c("WindSpeed", "Humidity", "Pressure", "Thermal"))

solar_clean_weather_test_hourly <- solar_clean_all %>%
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
  distinct(TimeDate, series_name, .keep_all = TRUE) %>%
  select(-start_timestamp,-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats, by= c("Date", "Hour")) #%>% select(-TimeDate, -contains(c("WindSpeed", "Humidity", "Pressure", "Thermal"))
```

```{r}
Hourly_WeatherData_Feats_Sep <- ERA_Feats %>%
  filter(TimeDate > "2020-09-01 09:00:00" & TimeDate < "2020-10-01 10:00:00") %>%
  dplyr::slice(rep(1:n(), each = 4)) %>%
  mutate(#Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         #Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         Year = year(TimeDate),
         Month =lubridate::month(TimeDate, label= TRUE),
         Day_of_Month = day(DateTime),
         Day = weekdays(Date),
         Week = week(TimeDate),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month, Day, Week, Hour, Minute, everything())

Hourly_WeatherData_Feats_Sep_building <- Hourly_WeatherData_Feats_Sep %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute,contains(c("Temperature")), -contains("Dew"))  
#DailyHourly_WeatherData_Feats_Oct_solar <- Daily_WeatherData_Feats_Oct_solar %>% left_join(ERA_Feats , by=c("Hour" ,"Date"))

Hourly_WeatherData_Feats_Sep_solar <- Hourly_WeatherData_Feats_Sep

```

```{r}
Hourly_WeatherData_Feats_Oct <- ERA_Feats %>%
  filter(TimeDate > "2020-10-01 09:00:00" & TimeDate < "2020-11-01 11:00:00") %>%
  dplyr::slice(rep(1:n(), each = 4)) %>%
  mutate(#Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 31*24), #which of the four 15 minutes block in one hour it is
         #Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         Year = year(TimeDate),
         Month =lubridate::month(TimeDate, label= TRUE),
         Day_of_Month = day(DateTime),
         Day = weekdays(Date),
         Week = week(TimeDate),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month, Day, Week, Hour, Minute, everything())


Hourly_WeatherData_Feats_Oct_building <- Hourly_WeatherData_Feats_Oct %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute,contains(c("Temperature")), -contains("Dew"))  
#DailyHourly_WeatherData_Feats_Oct_solar <- Daily_WeatherData_Feats_Oct_solar %>% left_join(ERA_Feats , by=c("Hour" ,"Date"))

Hourly_WeatherData_Feats_Oct_solar <- Hourly_WeatherData_Feats_Oct #%>%
  #select(-TimeDate)#, -contains(c("WindSpeed", "Humidity", "Pressure", "Thermal")))# %>% select(-contains("lag"), -contains("rolling"))
```

```{r}
Hourly_WeatherData_Feats_Nov <- ERA_Feats %>%
  filter(TimeDate > "2020-11-01 10:00:00" & TimeDate < "2020-12-01 11:00:00") %>%
  dplyr::slice(rep(1:n(), each = 4)) %>%
  mutate(#Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         #Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         Year = year(TimeDate),
         Month =lubridate::month(TimeDate, label= TRUE),
         Day_of_Month = day(DateTime),
         Day = weekdays(Date),
         Week = week(TimeDate),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month, Day, Week, Hour, Minute, everything())

Hourly_WeatherData_Feats_Nov_building <- Hourly_WeatherData_Feats_Nov %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute,contains(c("Temperature")), -contains("Dew"))  
#DailyHourly_WeatherData_Feats_Oct_solar <- Daily_WeatherData_Feats_Oct_solar %>% left_join(ERA_Feats , by=c("Hour" ,"Date"))

Hourly_WeatherData_Feats_Nov_solar <- Hourly_WeatherData_Feats_Nov
```


## Models with hourly data
```{r}
lgbm_mod_b0_f1mae_hourly <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building0") %>%
                     filter(Date>="2020-09-01" & Date< "2020-11-01") %>% #use this data for October/November
                     #filter(Date >="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly  %>% filter(series_name=="Building0") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 20,  
  max_depth = 9, 
  learning_rate = 0.1, 
  nrounds = 134, #9,  
  min_data_in_leaf = 200,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_b1_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix( building_clean_weather_train_hourly %>% filter(series_name=="Building1") %>%
                      as_tibble() %>% 
                      filter(Date< "2020-11-01") %>%
                      select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building1") %>% 
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,
  learning_rate = 0.1,
  max_depth = 9,
  nrounds = 105,#24,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 120,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1, ## adding this is useful
  verbose = -1)

lgbm_mod_b3_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building3") %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building3") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,
  max_depth = 8,
  learning_rate = 0.1,
  nrounds = 124L,
  min_data_in_leaf = 80,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b4_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building4")  %>%
                     as_tibble()  %>%
                     filter( Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building4")  %>%
    filter( Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 30L,  
  max_depth = 11,#9,  
  learning_rate = 0.1,  
  nrounds = 90,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7, 
  min_data_in_leaf = 50,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_b5_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building5") %>%
                     as_tibble() %>% filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
                     select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building5")  %>%
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
      pull(series_value),
  num_leaves = 50,  
  max_depth = 8,  
  learning_rate = 0.1,
  nrounds = 34,#4,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b6_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building6") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-01-01" & Date< "2020-11-01")%>%
                     select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building6") %>% 
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,
  learning_rate = 0.1,
  max_depth = 7,
  nrounds = 110,#9L, 
  min_data_in_leaf = 80,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# One-month LightGBM mod
lgbm_mod_s0_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar0") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%  
                     #filter(Date >= "2020-09-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -series_name, -contains("rolling"))),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar0")  %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date >= "2020-09-01") %>%
    pull(series_value),
  #force_row_wise = TRUE,
  num_leaves =50, # this is importnat too
  max_depth = 7,  
  learning_rate = 0.1, 
  nrounds = 222,#34,  
  min_data_in_leaf = 100, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_s1_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar1") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar1")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L,  
  max_depth = 11, 
  learning_rate = 0.1,  
  nrounds = 140,#22L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 300,  
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s2_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar2") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar2")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,  
  max_depth = 11, 
  learning_rate = 0.1, 
  nrounds = 110,#8L,  
  min_data_in_leaf = 150, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,
  verbose = -1)


lgbm_mod_s3_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar3")  %>%
                     as_tibble() %>% 
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
                     #filter(Date>= "2020-09-01") %>% #use this data for October/November
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar3") %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date>= "2020-09-01") %>%
    pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L,  
  max_depth = 10,  
  learning_rate = 0.1,  
  nrounds = 50,#20L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 50,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s4_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar4")  %>%
                     filter( Date< "2020-11-01") %>%
                     as_tibble() %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar4")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 250L,  
  max_depth = 13,  
  learning_rate = 0.1,  
  nrounds = 170,#15L, 
  min_data_in_leaf = 50,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_s5_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar5") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar5")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L, 
  max_depth = 8, 
  learning_rate = 0.1, 
  nrounds = 100,#10L,  
  min_data_in_leaf = 300,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)
```


## Prediction with hourly data
```{r}
# Read testSetForecastSpot
predict_lgbm_b0_f1mae_hourly <- predict(lgbm_mod_b0_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))
predict_lgbm_b1_f1mae_hourly <- predict(lgbm_mod_b1_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))
predict_lgbm_b3_f1mae_hourly <- predict(lgbm_mod_b3_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))
predict_lgbm_b4_f1mae_hourly <- predict(lgbm_mod_b4_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))
predict_lgbm_b5_f1mae_hourly <- predict(lgbm_mod_b5_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))
predict_lgbm_b6_f1mae_hourly <- predict(lgbm_mod_b6_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b_f1mae_hourly <- rbind(predict_lgbm_b0_f1mae_hourly, predict_lgbm_b1_f1mae_hourly, predict_lgbm_b3_f1mae_hourly, predict_lgbm_b4_f1mae_hourly, predict_lgbm_b5_f1mae_hourly, predict_lgbm_b6_f1mae_hourly)
predict_lgbm_b_f1mae_hourly[predict_lgbm_b_f1mae_hourly<0.01]=0
# Solar forecast October
predict_lgbm_s0_f1mae_hourly <- predict(lgbm_mod_s0_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar %>% select(-contains("rolling"))))
predict_lgbm_s1_f1mae_hourly <- predict(lgbm_mod_s1_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))
predict_lgbm_s2_f1mae_hourly <- predict(lgbm_mod_s2_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))
predict_lgbm_s3_f1mae_hourly <- predict(lgbm_mod_s3_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))
predict_lgbm_s4_f1mae_hourly <- predict(lgbm_mod_s4_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))
predict_lgbm_s5_f1mae_hourly <- predict(lgbm_mod_s5_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s_f1mae_hourly <- rbind(predict_lgbm_s0_f1mae_hourly, predict_lgbm_s1_f1mae_hourly, predict_lgbm_s2_f1mae_hourly, predict_lgbm_s3_f1mae_hourly, predict_lgbm_s4_f1mae_hourly, predict_lgbm_s5_f1mae_hourly)
predict_lgbm_s_f1mae_hourly[predict_lgbm_s_f1mae_hourly<0.15]=0
```


```{r}
predict_sb_h <- rbind(predict_lgbm_b_f1mae_hourly,predict_lgbm_s_f1mae_hourly)
rownames(predict_sb_h) <- c(buildings, solars)
write.csv(predict_sb_h, "i2h-Nov.csv")
```

Final forecast used in the competition. 
```{r}
psb <- (predict_sb_h + predict_sb_daily)/2
```

```{r}
bind_rows(tsibble_data_Oct  %>% as_tibble() %>% 
    select(TimeDate,series_value,series_name),predict_sb_daily %>% t() %>% as_tibble()  %>% 
    pivot_longer(cols= c(1:12),names_to = "series_name", values_to= "series_value") %>%
    mutate(h= rep((1:2880), each=12))) %>%
    filter(series_name == "Building0") %>% pull(series_value) %>% plot.ts()

```


```{r}
# lightgbm::lgb.save(lgbm_mod_b0_f1mae, "lgbm_mod_b0_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_b1_f1mae , "lgbm_mod_b1_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_b3_f1mae , "lgbm_mod_b3_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_b4_f1mae , "lgbm_mod_b4_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_b5_f1mae , "lgbm_mod_b5_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_b6_f1mae , "lgbm_mod_b6_f1mae_hourly_sep.txt")
# 
 lightgbm::lgb.save(lgbm_mod_s0_f1mae_hourly , "lgbm_mod_s0_f1mae_hourly_oct.txt")
# lightgbm::lgb.save(lgbm_mod_s1_f1mae , "lgbm_mod_s1_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_s2_f1mae , "lgbm_mod_s2_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_s3_f1mae , "lgbm_mod_s3_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_s4_f1mae , "lgbm_mod_s4_f1mae_hourly_sep.txt")
# lightgbm::lgb.save(lgbm_mod_s5_f1mae , "lgbm_mod_s5_f1mae_hourly_sep.txt")

lgbm_mod_b0_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b0_f1mae_hourly_oct.txt"))
lgbm_mod_b1_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b1_f1mae_hourly_oct.txt"))
lgbm_mod_b3_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b3_f1mae_hourly_oct.txt"))
lgbm_mod_b4_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b4_f1mae_hourly_oct.txt"))
lgbm_mod_b5_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b5_f1mae_hourly_oct.txt"))
lgbm_mod_b6_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_b6_f1mae_hourly_oct.txt"))

lgbm_mod_s0_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s0_f1mae_hourly_oct.txt"))
lgbm_mod_s1_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s1_f1mae_hourly_oct.txt"))
lgbm_mod_s2_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s2_f1mae_hourly_oct.txt"))
lgbm_mod_s3_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s3_f1mae_hourly_oct.txt"))
lgbm_mod_s4_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s4_f1mae_hourly_oct.txt"))
lgbm_mod_s5_f1mae_hourly <- lightgbm::lgb.load(here::here("Models","lgbm_mod_s5_f1mae_hourly_oct.txt"))
```


## Creating daily-hourly data

```{r}
building_clean_weather_daily_hourly <- building_clean_all %>% 
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,series_name, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(Date, Hour, contains("Temperature"), -contains("Dew")), by= c("Date", "Hour"))  %>%
    distinct_at(vars(series_name, TimeDate), .keep_all = TRUE) %>%
left_join(building_clean_weather_daily %>% select(-Year, -Date, -Season,-series_value, -Month, -Week, -Day_of_Month,-Day, -Hour, -Minute) %>%  distinct_at(vars(series_name, TimeDate), .keep_all = TRUE), by= c("TimeDate","series_name"))

building_clean_weather_train_daily_hourly <- building_clean_weather_daily_hourly %>% 
  filter(Date < "2020-11-01") %>% select(-contains("Expo"))

building_clean_weather_test_daily_hourly <- building_clean_weather_daily_hourly %>% 
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>% select(-contains("Expo")) %>%
  replace_with_na(list(series_value=1744.1)) ## this is the big outlier in
```


```{r}
solar_clean_weather_daily_hourly <- solar_clean_all %>% 
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,series_name, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(-TimeDate), by= c("Date", "Hour"))  %>%
  distinct_at(vars(series_name, TimeDate), .keep_all = TRUE) %>%
  left_join(solar_clean_weather_daily %>% select(-Year, -Date, -Season,-series_value, -Month, -Week, -Day_of_Month,-Day, -Hour, -Minute) %>%  distinct_at(vars(series_name, TimeDate), .keep_all = TRUE), by= c("TimeDate","series_name"))

solar_clean_weather_train_daily_hourly <- solar_clean_weather_daily_hourly %>% 
  filter(Date < "2020-11-01") %>%    select(-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)


solar_clean_weather_test_daily_hourly <- solar_clean_weather_daily_hourly %>% 
  filter(Date >= "2020-09-01" & Date < "2020-11-01")
```


```{r}
saveRDS(solar_clean_weather_train_daily_hourly, "solar_clean_weather_train_daily_hourly.rds")
saveRDS(building_clean_weather_train_daily_hourly, "building_clean_weather_train_daily_hourly.rds")
saveRDS(solar_clean_weather_train_hourly, "solar_clean_weather_train_hourly.rds")
saveRDS(building_clean_weather_train_hourly, "building_clean_weather_train_hourly.rds")
saveRDS(solar_clean_weather_train_daily, "solar_clean_weather_train_daily.rds")
saveRDS(building_clean_weather_train_daily, "building_clean_weather_train_daily.rds")

```

```{r}
saveRDS(solar_clean_weather_test_daily_hourly, "solar_clean_weather_test_daily_hourly.rds")
saveRDS(building_clean_weather_test_daily_hourly, "building_clean_weather_test_daily_hourly.rds")
saveRDS(solar_clean_weather_test_hourly, "solar_clean_weather_test_hourly.rds")
saveRDS(building_clean_weather_test_hourly, "building_clean_weather_test_hourly.rds")
saveRDS(solar_clean_weather_test_daily, "solar_clean_weather_test_daily.rds")
saveRDS(building_clean_weather_test_daily, "building_clean_weather_test_daily.rds")
```


```{r}
Daily_hourly_WeatherData_Feats_Nov_solar <- Daily_WeatherData_Feats_Nov_solar %>% select(contains(c("Avg", "_day"))) %>% bind_cols(Hourly_WeatherData_Feats_Nov_solar) %>% 
    select(Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute, everything()) %>%
    select(-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)



Daily_hourly_WeatherData_Feats_Nov_building <-  Daily_WeatherData_Feats_Nov_building %>% select(contains(c("Avg", "_day"))) %>% bind_cols(Hourly_WeatherData_Feats_Nov_building) %>%
      select(Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute, everything())
```

## Models and Predictions with daily hourly data

```{r}
lgbm_mod_b0_f1mae_daily_hourly <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily_hourly %>% filter(series_name=="Building0") %>%
                     filter(Date>="2020-09-01" & Date< "2020-11-01") %>% #use this data for October/November
                     #filter(Date >="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>%
                     select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly  %>% filter(series_name=="Building0") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 20,  
  max_depth = 7, 
  learning_rate = 0.1, 
  nrounds = 48, #9,  
  min_data_in_leaf = 50,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_b1_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix( building_clean_weather_train_daily_hourly %>% filter(series_name=="Building1") %>%
                      as_tibble() %>% 
                      filter(Date< "2020-11-01") %>%
                      select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly %>% filter(series_name=="Building1") %>% 
    filter(Date< "2020-11-01") %>% pull(series_value),
  #force_row_wise = TRUE,
  num_leaves = 180L,
  learning_rate = 0.1,
  max_depth = 12,
  nrounds = 50,#24,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 80,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1, ## adding this is useful
  verbose = -1)

lgbm_mod_b3_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily_hourly %>% filter(series_name=="Building3") %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>% select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly %>% filter(series_name=="Building3") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  #force_row_wise = TRUE,
  num_leaves = 100L,
  max_depth = 8,
  learning_rate = 0.1,
  nrounds = 42L,
  min_data_in_leaf = 80,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b4_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily_hourly %>% filter(series_name=="Building4")  %>%
                     as_tibble()  %>%
                     filter( Date< "2020-11-01") %>% 
                     select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly %>% filter(series_name=="Building4")  %>%
    filter( Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 30L,  
  max_depth = 9,#9,  
  learning_rate = 0.1,  
  nrounds = 50,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7, 
  min_data_in_leaf = 50,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_b5_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily_hourly %>% filter(series_name=="Building5") %>%
                     as_tibble() %>% filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
                     select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly %>% filter(series_name=="Building5")  %>%
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
    pull(series_value),
  num_leaves = 80,  
  max_depth = 7,  
  learning_rate = 0.1,
  nrounds = 12,#4,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 50,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b6_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily_hourly %>% filter(series_name=="Building6") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-01-01" & Date< "2020-11-01")%>%
                     select(-start_timestamp,-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily_hourly %>% filter(series_name=="Building6") %>% 
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>% pull(series_value),
  #force_row_wise = TRUE,
  num_leaves = 80L,
  learning_rate = 0.1,
  max_depth = 10,
  nrounds = 20,#9L, 
  min_data_in_leaf = 150,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# One-month LightGBM mod
lgbm_mod_s0_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar0") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%  
                     #filter(Date >= "2020-09-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -series_name, -TimeDate, -contains("rolling"))),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar0")  %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date >= "2020-09-01") %>%
    pull(series_value),
  #force_row_wise = TRUE,
  num_leaves =30, # this is importnat too
  max_depth = 11,  
  learning_rate = 0.1, 
  nrounds = 204,#34,  
  min_data_in_leaf = 200, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_s1_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar1") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar1")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 50L,  
  max_depth = 7, 
  learning_rate = 0.1,  
  nrounds = 130,#22L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 120,  
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s2_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar2") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -TimeDate, -series_name)),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar2")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 80L,  
  max_depth = 10, 
  learning_rate = 0.1, 
  nrounds = 64,#8L,  
  min_data_in_leaf = 300, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,
  verbose = -1)


lgbm_mod_s3_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar3")  %>%
                     as_tibble() %>% 
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
                     #filter(Date>= "2020-09-01") %>% #use this data for October/November
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -TimeDate, -series_name)),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar3") %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date>= "2020-09-01") %>%
    pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L,  
  max_depth = 7,  
  learning_rate = 0.1,  
  nrounds = 280,#20L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 80,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s4_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar4")  %>%
                     filter( Date< "2020-11-01") %>%
                     as_tibble() %>% select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar4")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,  
  max_depth = 8,  
  learning_rate = 0.1,  
  nrounds = 58,#15L, 
  min_data_in_leaf = 50,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_s5_f1mae_daily_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar5") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily_hourly %>% filter(series_name=="Solar5")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 80L, 
  max_depth = 10, 
  learning_rate = 0.1, 
  nrounds = 83,#10L,  
  min_data_in_leaf = 50,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)
```

```{r, eval=FALSE}
predict_lgbm_b0_f1mae_daily_hourly <- predict(lgbm_mod_b0_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building0") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b1_f1mae_daily_hourly <- predict(lgbm_mod_b1_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building1") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b3_f1mae_daily_hourly <- predict(lgbm_mod_b3_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building3") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b4_f1mae_daily_hourly <- predict(lgbm_mod_b4_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building4") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b5_f1mae_daily_hourly <- predict(lgbm_mod_b5_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building5") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b6_f1mae_daily_hourly <- predict(lgbm_mod_b6_f1mae_daily_hourly, as.matrix(building_clean_weather_test_daily_hourly %>% filter(series_name=="Building6") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_b_f1mae_daily_hourly <- rbind(predict_lgbm_b0_f1mae_daily_hourly, predict_lgbm_b1_f1mae_daily_hourly, predict_lgbm_b3_f1mae_daily_hourly, predict_lgbm_b4_f1mae_daily_hourly, predict_lgbm_b5_f1mae_daily_hourly, predict_lgbm_b6_f1mae_daily_hourly)

# Solar forecast October
predict_lgbm_s0_f1mae_daily_hourly <- predict(lgbm_mod_s0_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar0") %>% select(-series_name, -series_value,-contains("rolling")) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s1_f1mae_daily_hourly <- predict(lgbm_mod_s1_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar1") %>% select(-series_name, -series_value)%>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s2_f1mae_daily_hourly <- predict(lgbm_mod_s2_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar3") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s3_f1mae_daily_hourly <- predict(lgbm_mod_s3_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar3") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s4_f1mae_daily_hourly <- predict(lgbm_mod_s4_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar4") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s5_f1mae_daily_hourly <- predict(lgbm_mod_s5_f1mae_daily_hourly, as.matrix(solar_clean_weather_test_daily_hourly %>% filter(series_name=="Solar5") %>% select(-series_name, -series_value) %>%  filter(Date>="2020-10-01" & Date< "2020-11-01")))

predict_lgbm_s_f1mae_daily_hourly <- rbind(predict_lgbm_s0_f1mae_daily_hourly, predict_lgbm_s1_f1mae_daily_hourly, predict_lgbm_s2_f1mae_daily_hourly, predict_lgbm_s3_f1mae_daily_hourly, predict_lgbm_s4_f1mae_daily_hourly, predict_lgbm_s5_f1mae_daily_hourly)

# turn small values to zero
predict_lgbm_s_f1mae_daily_hourly[predict_lgbm_s_f1mae_daily_hourly<0.1]=0
predict_lgbm_b_f1mae_daily_hourly[predict_lgbm_b_f1mae_daily_hourly<0.01]=0
```


```{r}
predict_lgbm_b0_f1mae_daily_hourly <- predict(lgbm_mod_b0_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b1_f1mae_daily_hourly <- predict(lgbm_mod_b1_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b3_f1mae_daily_hourly <- predict(lgbm_mod_b3_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b4_f1mae_daily_hourly <- predict(lgbm_mod_b4_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b5_f1mae_daily_hourly <- predict(lgbm_mod_b5_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b6_f1mae_daily_hourly <- predict(lgbm_mod_b6_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b_f1mae_daily_hourly <- rbind(predict_lgbm_b0_f1mae_daily_hourly, predict_lgbm_b1_f1mae_daily_hourly, predict_lgbm_b3_f1mae_daily_hourly, predict_lgbm_b4_f1mae_daily_hourly, predict_lgbm_b5_f1mae_daily_hourly, predict_lgbm_b6_f1mae_daily_hourly)

# Solar forecast October
predict_lgbm_s0_f1mae_daily_hourly <- predict(lgbm_mod_s0_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar %>% select(-contains("rolling"))))

predict_lgbm_s1_f1mae_daily_hourly <- predict(lgbm_mod_s1_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s2_f1mae_daily_hourly <- predict(lgbm_mod_s2_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s3_f1mae_daily_hourly <- predict(lgbm_mod_s3_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s4_f1mae_daily_hourly <- predict(lgbm_mod_s4_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s5_f1mae_daily_hourly <- predict(lgbm_mod_s5_f1mae_daily_hourly, as.matrix(Daily_hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s_f1mae_daily_hourly <- rbind(predict_lgbm_s0_f1mae_daily_hourly, predict_lgbm_s1_f1mae_daily_hourly, predict_lgbm_s2_f1mae_daily_hourly, predict_lgbm_s3_f1mae_daily_hourly, predict_lgbm_s4_f1mae_daily_hourly, predict_lgbm_s5_f1mae_daily_hourly)

# turn small values to zero
predict_lgbm_s_f1mae_daily_hourly[predict_lgbm_s_f1mae_daily_hourly<0.1]=0
predict_lgbm_b_f1mae_daily_hourly[predict_lgbm_b_f1mae_daily_hourly<0.01]=0
```

```{r}
predict_sb_daily_hourly <- rbind(predict_lgbm_b_f1mae_daily_hourly,predict_lgbm_s_f1mae_daily_hourly)
rownames(predict_sb_daily_hourly) <- c(buildings, solars)
write.csv(predict_sb_daily_hourly, "i3-Nov.csv")

```


### Variable importance Solars
```{r}
# Feature importance
lgbm_ImpVar_s0 <- lightgbm::lgb.importance(lgbm_mod_s0, percentage = TRUE)
lgbm_ImpVar_s1 <- lightgbm::lgb.importance(lgbm_mod_s1, percentage = TRUE)
lgbm_ImpVar_s2 <- lightgbm::lgb.importance(lgbm_mod_s2, percentage = TRUE)
lgbm_ImpVar_s3 <- lightgbm::lgb.importance(lgbm_mod_s3, percentage = TRUE)
lgbm_ImpVar_s4 <- lightgbm::lgb.importance(lgbm_mod_s4, percentage = TRUE)
lgbm_ImpVar_s5 <- lightgbm::lgb.importance(lgbm_mod_s5, percentage = TRUE)

# View feature importance rank
lgbm_ImpVar_s0 %>%
  as_tibble() %>%
  ggplot(aes(x = fct_reorder(Feature, Gain), y = Gain)) +
  geom_col(alpha = 0.8) +
  labs(title = "Feature importances ranking",
       x = "Features") +
  coord_flip() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.border = element_blank(),
  axis.line = element_line())
```

