---
title: "Solar-Demand_Energy_Forecasting"
author: "Mahdi Abolghasemi"
date: "30/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=6)
options(scipen = 999)
theme_set(theme_bw())

# Load required packages
library(tidyverse)
library(scales)
library(lubridate)
library(tsibble)
library(cowplot)
library(visdat)
library(naniar)
library(viridis)
library(ggExtra)
library(mgcv)
library(naniar)
library(visdat)
library(plotly)
library(purrr)
library(chron)
library(ggrepel)
library(reshape2)
library(forecast)
library(ggthemes)
library(scales)
library(gridExtra)
library(grid)
library(fable)
library(openair)
library(ggmap)
library(lemon)
library(formattable)
library(Hmisc)
library(corrplot)
library(lattice)
library(knitr)
library(kableExtra)
library(feasts)
library(furrr)
library(sugrrants)
library(tidymodels)
library(here)
library(lightgbm)
library(oce)
library(openair)
```

# Reading solar and building data
We created calendar features and save it in the following objects, so we can use it from here on.
```{r, echo=FALSE}
#saveRDS(tsibble_data_Oct, "tsibble_data_Oct.rds")
tsibble_data_Oct <- read_rds(here::here("Data","tsibble_data_Oct.rds"))

#saveRDS(tsibble_data_All, "tsibble_data_All_UTC.rds")
tsibble_data_All <- read_rds(here::here("Data", "tsibble_data_All_UTC.rds"))
```

```{r}
#defining solars and buildingsseries
solars <- c("Solar0", "Solar1", "Solar2", "Solar3", "Solar4", "Solar5")
buildings <- c("Building0", "Building1", "Building3", "Building4", "Building5", "Building6")
```

We run preprocessing on building and solar data to clean up the missing values, choose the relevant observations, and save the final data.  We check for outliers, negative, missing values. We can see that there are lots of missing values across both solars and buildings data. After an extensive analysis and running several experiments, we removed missing values from our series. `building_clean_all` is the subset of building data, and `solar_clean_all` is the subset of solar data. The final data are saved and can be read below. 

```{r}
# saveRDS(solar_clean_all, "solar_clean_all.rds")
# saveRDS(building_clean_all, "building_clean_all.rds")
solar_clean_all <- read_rds(here::here("Data", "solar_clean_all.rds"))
building_clean_all <- read_rds(here::here("Data","building_clean_all.rds"))
building_clean_all <- building_clean_all %>% replace_with_na(list(series_value=1744.1))
```


# Reading weather data

We downloaded solar, rain fall, max and min temperature from BOM. These data sets are recorded for each day which may not be ideal for our forecasting as we generate forecast for each 15 minute time slot. We do feature engineering on data. The final data is saved and can be loaded using the script below.

```{r}
#saveRDS(Weather_data, "Weather_data.rds")
Weather_data <- read_rds(here::here("Data", "Weather_data.rds"))
```

## Feature Engineering daily and houlry weather data

We conduct extensive feature engineering and create various rolling features for weather data. The final daily weather data is stored and can be read below.
```{r}
#saveRDS(Daily_WeatherData_Feats, "Daily_WeatherData_Feats.rds")
Daily_WeatherData_Feats <- read_rds(here::here("Data","Daily_WeatherData_Feats.rds"))
```

The final hourly data is stored below. 
```{r}
#saveRDS(ERA_Feats,here("Data", "ERA_Feats.RDS"))
ERA_Feats <- read_rds(here::here("Data", "ERA_Feats.rds"))
```


# Joining data and creating required data for buildings and solars series using daily and hourly data

We don't need to read the next two chunks, but in case needed this chunk merges the required data that is saved and loaded above.

```{r train-data_building, eval=FALSR}
# building_clean_weather_daily <- building_clean_all %>% 
 # left_join(Daily_WeatherData_Feats %>% select(-Day, -Year, -Month, -(contains("lag"))), by= c("Date"="index"))

#building_clean_weather_train_daily <- building_clean_weather_daily %>%
 #   filter(Date < "2020-11-01") %>%
  #  select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
  # select(-start_timestamp,-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day)

#building_clean_weather_test_daily <- building_clean_weather_daily %>%
  #filter((Date) >= "2020-09-01" & Date < "2020-11-01") %>% 
 # distinct(TimeDate,series_name, .keep_all = TRUE) %>%
#select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>% select(-start_timestamp,-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day)
```

```{r train-data_solars, eval=FALSE}
# solar_clean_weather_daily <- solar_clean_all %>% 
 # left_join(Daily_WeatherData_Feats %>% select(-Day, -Year, -Month, -(contains("lag"))), by= c("Date"="index"))

#solar_clean_weather_train_daily <- solar_clean_weather_daily %>%
  #  filter(Date < "2020-11-01") %>%
 #   select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
 #   select(-start_timestamp,-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)

#solar_clean_weather_test_daily <- solar_clean_weather_daily %>%
#  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
#  distinct(TimeDate,series_name, .keep_all = TRUE) %>%
#   select(-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute,everything()) %>%
 # select(-start_timestamp,-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day)
```

The final data are stored and read below:
```{r}
solar_clean_weather_train_hourly <- readRDS(here::here("Data","solar_clean_weather_train_hourly.rds"))
building_clean_weather_train_hourly <- readRDS(here::here("Data","building_clean_weather_train_hourly.rds"))

solar_clean_weather_train_daily <- readRDS(here::here("Data","solar_clean_weather_train_daily.rds"))
building_clean_weather_train_daily <- readRDS(here::here("Data","building_clean_weather_train_daily.rds"))
```

```{r}
solar_clean_weather_test_hourly <- readRDS(here::here("Data","solar_clean_weather_test_hourly.rds"))
building_clean_weather_test_hourly <- readRDS(here::here("Data","building_clean_weather_test_hourly.rds"))

solar_clean_weather_test_daily <- readRDS(here::here("Data","solar_clean_weather_test_daily.rds"))
building_clean_weather_test_daily <- readRDS(here::here("Data","building_clean_weather_test_daily.rds"))
```

We need to create rolling features of weather data for November exactly same as the feature engineering done on feature engineered , so that it will be used as inputs of the forecasting models used for building and solar series separately. 

```{r}
Daily_WeatherData_Feats_Nov_building <- Daily_WeatherData_Feats %>% 
   select(-Avg_Exposure, -SolarExpo_rollingMean_2_day, -SolarExpo_rollingSd_3_day) %>%
  select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-11-01" & index <"2020-12-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 30),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```

```{r}
Daily_WeatherData_Feats_Nov_solar <- Daily_WeatherData_Feats %>%  
  ##### NOTE-IMPORTANT### This is only needed for dailyhourly, for daily it must be deactivated
  select(-RainFall_rollingMean_2_day, -RainFall_rollingSd_3_day) %>% 
   select(-Day, Year, -Month, -(contains("lag"))) %>%
  filter(index>="2020-11-01" & index <"2020-12-01") %>%
  dplyr::slice(rep(1:n(), each = 24*4)) %>%  
  mutate(Hour = rep(rep(c(0:23), each=4), 30),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         #Year = year(start_timestamp), 
         Month =lubridate::month(index, label= TRUE), 
         Day_of_Month = day(index),
         Day = weekdays(index),
         Week = week(index),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute, everything()) %>% select(-index)
```


## Models and Predictions with daily data

```{r}
lgbm_mod_b0_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01") %>% #use this data for October/November
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Building0") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
    filter(series_name=="Building0") %>% pull(series_value),
  num_leaves = 20L, 
  max_depth = 10, 
  learning_rate = 0.1,  
  nrounds = 80,  
  #feature_fraction = 0.8, # not useful
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_b1_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix( building_clean_weather_train_daily %>% filter(series_name=="Building1") %>%
                      as_tibble()  %>% 
                      filter(Date < "2020-11-01") %>% select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily %>% filter(series_name=="Building1")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100,
  max_depth = 9,
  learning_rate = 0.1,
  nrounds = 120,
  #max_bin = 550L,
  min_data_in_leaf = 120,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_b3_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01")%>% 
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Building3") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>% 
    filter(series_name=="Building3") %>% pull(series_value),
  num_leaves = 20L,  
  max_depth = 10,  
  learning_rate = 0.1,  
  nrounds = 120,  
  #feature_fraction = 0.7, 
  min_data_in_leaf = 80,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)

lgbm_mod_b4_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily %>% filter(series_name=="Building4")  %>% 
                     filter( Date < "2020-11-01") %>%
                     as_tibble() %>% select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily %>% filter(series_name=="Building4")  %>% 
    filter(Date < "2020-11-01")%>% pull(series_value),
  num_leaves = 80L, 
  max_depth = 7,  
  learning_rate = 0.1,  
  nrounds = 30L, 
  #feature_fraction = 0.7,  
  min_data_in_leaf = 300,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_b5_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date < "2020-11-01") %>% #Date>"2020-01-01" & 
                     filter(series_name=="Building5") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily   %>% 
    filter(Date < "2020-11-01") %>% #Date>"2020-01-01" & 
    filter(series_name=="Building5") %>% pull(series_value),
  num_leaves = 52, #200L,  
  max_depth = 8,  
  learning_rate = 0.1, #0.1,   
  nrounds = 25L,  
  #feature_fraction = 0.7,
  min_data_in_leaf = 50, #180,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_b6_f1mae_daily <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_daily  %>% 
                     filter(Date>"2020-01-01" & Date < "2020-11-01") %>% 
                     filter(series_name=="Building6") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = building_clean_weather_train_daily  %>% 
    filter(Date>"2020-01-01" & Date < "2020-11-01") %>%
    filter(series_name=="Building6") %>% pull(series_value),
  num_leaves = 30L,  
  max_depth = 7, 
  learning_rate = 0.1,  
  nrounds = 30L, 
  #feature_fraction = 1,  
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",
  lambda_l1 = 0.1, 
  verbose = -1)

# One-month LightGBM mod
lgbm_mod_s0_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar0")  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-contains("rolling"))%>%
                     as_tibble() %>% select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01") %>%
    select(-contains("rolling"))%>%
    filter(series_name=="Solar0") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L, 
  max_depth = 9,
  learning_rate = 0.1,
  nrounds = 100L,
  #max_bin = 550L,# not useful 
  #feature_fraction = 0.8, # not useful
  min_data_in_leaf = 50,
  objective = "mae",
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = .1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_s1_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar1") %>%
                     as_tibble()%>% 
                     filter(Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar1")  %>% 
    filter( Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,  
  max_depth = 8,  
  learning_rate = 0.1, 
  nrounds = 85L,
  #feature_fraction = 0.7,  
  min_data_in_leaf = 250, 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s2_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar2") %>%
                     as_tibble()  %>% 
                     filter( Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar2")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,  
  max_depth = 7,  
  learning_rate = 0.1,  
  nrounds = 80L, 
 # feature_fraction = 0.7,  
  min_data_in_leaf = 50,   
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.2,  
  verbose = -1)


lgbm_mod_s3_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily  %>% 
                     filter(Date>"2020-09-01" & Date < "2020-11-01")%>% 
                     #filter(Date>"2020-08-01") %>% #use this date for sep test
                     filter(series_name=="Solar3") %>% as_tibble() %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily  %>% 
    filter(Date>"2020-09-01" & Date < "2020-11-01")%>%
    filter(series_name=="Solar3") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L, 
  max_depth = 7, 
  learning_rate = 0.1, 
  nrounds = 70L,  
 # feature_fraction = 0.7,  
  min_data_in_leaf = 50,  
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)


lgbm_mod_s4_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar4") %>%
                     as_tibble()  %>% 
                     filter(Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar4")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 180L, 
  max_depth = 12, 
  learning_rate = 0.1,  
  nrounds = 40L,  
  #feature_fraction = 0.7,  
  min_data_in_leaf = 50, # 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)

lgbm_mod_s5_f1mae_daily  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_daily %>% filter(series_name=="Solar5") %>%
                     as_tibble()  %>% 
                     filter( Date < "2020-11-01") %>%
                     select(-series_value, -series_name, -TimeDate)),
  label = solar_clean_weather_train_daily %>% filter(series_name=="Solar5")  %>% 
    filter(Date < "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 80L,  
  max_depth = 10,  
  learning_rate = 0.1, 
  nrounds = 37, 
  #feature_fraction = 0.7,  
  min_data_in_leaf = 300, 
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)
```

Predictions for November using dailt data are generated below.
```{r}
predict_lgbm_b0_f1mae_daily <- predict(lgbm_mod_b0_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b1_f1mae_daily <- predict(lgbm_mod_b1_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b3_f1mae_daily <- predict(lgbm_mod_b3_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b4_f1mae_daily <- predict(lgbm_mod_b4_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b5_f1mae_daily <- predict(lgbm_mod_b5_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b6_f1mae_daily <- predict(lgbm_mod_b6_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_building))

predict_lgbm_b_f1mae_daily <- rbind(predict_lgbm_b0_f1mae_daily, predict_lgbm_b1_f1mae_daily, predict_lgbm_b3_f1mae_daily, predict_lgbm_b4_f1mae_daily, predict_lgbm_b5_f1mae_daily, predict_lgbm_b6_f1mae_daily)

# Solar forecast 
predict_lgbm_s0_f1mae_daily <- predict(lgbm_mod_s0_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar %>% select(-contains("rolling"))))

predict_lgbm_s1_f1mae_daily <- predict(lgbm_mod_s1_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s2_f1mae_daily <- predict(lgbm_mod_s2_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s3_f1mae_daily <- predict(lgbm_mod_s3_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s4_f1mae_daily <- predict(lgbm_mod_s4_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s5_f1mae_daily <- predict(lgbm_mod_s5_f1mae_daily, as.matrix(Daily_WeatherData_Feats_Nov_solar))

predict_lgbm_s_f1mae_daily <- rbind(predict_lgbm_s0_f1mae_daily, predict_lgbm_s1_f1mae_daily, predict_lgbm_s2_f1mae_daily, predict_lgbm_s3_f1mae_daily, predict_lgbm_s4_f1mae_daily, predict_lgbm_s5_f1mae_daily)

# turn small values to zero
predict_lgbm_s_f1mae_daily[predict_lgbm_s_f1mae_daily<0.15]=0
predict_lgbm_b_f1mae_daily[predict_lgbm_b_f1mae_daily<0.01]=0
```


```{r}
predict_sb_daily <- rbind(predict_lgbm_b_f1mae_daily,predict_lgbm_s_f1mae_daily)
rownames(predict_sb_daily) <- c(buildings, solars)
#write.csv(predict_sb_daily, "i2d-Nov.csv")
```

## Developing models with hourly data

```{r}
building_clean_weather_train_hourly <- building_clean_all %>% 
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,series_name, -TimeDate, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(Date, Hour, contains("Temperature"), -contains("Dew")), by= c("Date", "Hour")) 

building_clean_weather_test_hourly <- building_clean_all %>% 
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
  distinct(TimeDate, series_name, .keep_all = TRUE) %>%
  select(-start_timestamp,series_name, -TimeDate, Year, Date, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats %>% select(Date, Hour, contains("Temperature"), -contains("Dew")), by= c("Date", "Hour")) %>%
  replace_with_na(list(series_value=1744.1)) ## this is the big outlier in
 

solar_clean_weather_train_hourly <- solar_clean_all %>%
  filter(Date < "2020-11-01") %>%
  select(-start_timestamp,-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats, by= c("Date", "Hour")) #%>% select(-TimeDate, -contains(c("WindSpeed", "Humidity", "Pressure", "Thermal"))

solar_clean_weather_test_hourly <- solar_clean_all %>%
  filter(Date >= "2020-09-01" & Date < "2020-11-01") %>%
  distinct(TimeDate, series_name, .keep_all = TRUE) %>%
  select(-start_timestamp,-TimeDate, series_name, Year, Season, Month, Week, Day_of_Month,Day, Hour, Minute) %>%
  left_join(ERA_Feats, by= c("Date", "Hour")) #%>% select(-TimeDate, -contains(c("WindSpeed", "Humidity", "Pressure", "Thermal"))
```


```{r}
Hourly_WeatherData_Feats_Nov <- ERA_Feats %>%
  filter(TimeDate >= "2020-11-01 03:30:00" & TimeDate < "2020-12-01 03:30:00") %>%
  dplyr::slice(rep(1:n(), each = 4)) %>%
  mutate(#Hour = rep(rep(c(0:23), each=4), 31),
         #series_name = as.character(series_name),
         Minute = rep(c(0,15,30,45), 30*24), #which of the four 15 minutes block in one hour it is
         #Date = date(index),
         #TimeDate = lubridate::ymd_hms(paste0(index, Hour, Minute)),
         Year = year(TimeDate),
         Month =lubridate::month(TimeDate, label= TRUE),
         Day_of_Month = day(DateTime),
         Day = weekdays(Date),
         Week = week(TimeDate),
         Season = case_when(
           Month %in% c("Dec", "Jan", "Feb") ~ 1,
           Month %in% c("Mar", "Apr", "May") ~ 2,
           Month %in% c("Jun", "Jul", "Aug") ~ 3,
           Month %in% c("Sep", "Oct", "Nov")  ~ 4),
         Day = case_when(
           Day == "Monday" ~ 1,
           Day == "Tuesday" ~ 2,
           Day == "Wednesday" ~ 3,
           Day == "Thursday" ~ 4,
           Day == "Friday" ~ 5,
           Day == "Saturday" ~ 6,
           Day == "Sunday" ~ 7)
         ) %>% as_tibble() %>%
  select(Date, Year, Season, Month, Day_of_Month, Day, Week, Hour, Minute, everything())

Hourly_WeatherData_Feats_Nov_building <- Hourly_WeatherData_Feats_Nov %>%
  select(Date, Year, Season, Month, Day_of_Month,Day, Week, Hour, Minute,contains(c("Temperature")), -contains("Dew"))

Hourly_WeatherData_Feats_Nov_solar <- Hourly_WeatherData_Feats_Nov
```


## Models with hourly data

```{r}
lgbm_mod_b0_f1mae_hourly <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building0") %>%
                     filter(Date>="2020-09-01" & Date< "2020-11-01") %>% #use this data for October/November
                     #filter(Date >="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly  %>% filter(series_name=="Building0") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 20,  
  max_depth = 9, 
  learning_rate = 0.1, 
  nrounds = 134, #9,  
  min_data_in_leaf = 200,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_b1_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix( building_clean_weather_train_hourly %>% filter(series_name=="Building1") %>%
                      as_tibble() %>% 
                      filter(Date< "2020-11-01") %>%
                      select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building1") %>% 
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,
  learning_rate = 0.1,
  max_depth = 9,
  nrounds = 105,#24,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 120,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1, ## adding this is useful
  verbose = -1)

lgbm_mod_b3_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building3") %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     as_tibble() %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building3") %>%
    filter(Date>="2020-09-01" & Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 100L,
  max_depth = 8,
  learning_rate = 0.1,
  nrounds = 124L,
  min_data_in_leaf = 80,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",
  num_threads = 8, 
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b4_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building4")  %>%
                     as_tibble()  %>%
                     filter( Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building4")  %>%
    filter( Date< "2020-11-01") %>% pull(series_value),
  num_leaves = 30L,  
  max_depth = 11,#9,  
  learning_rate = 0.1,  
  nrounds = 90,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7, 
  min_data_in_leaf = 50,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_b5_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building5") %>%
                     as_tibble() %>% filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
                     select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building5")  %>%
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>%
      pull(series_value),
  num_leaves = 50,  
  max_depth = 8,  
  learning_rate = 0.1,
  nrounds = 34,#4,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 150,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)

lgbm_mod_b6_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(building_clean_weather_train_hourly %>% filter(series_name=="Building6") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-01-01" & Date< "2020-11-01")%>%
                     select(-series_value, -series_name)),
  label = building_clean_weather_train_hourly %>% filter(series_name=="Building6") %>% 
    filter(Date >= "2020-01-01" & Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,
  learning_rate = 0.1,
  max_depth = 7,
  nrounds = 110,#9L, 
  min_data_in_leaf = 80,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


# One-month LightGBM mod
lgbm_mod_s0_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar0") %>%
                     as_tibble()  %>%
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%  
                     #filter(Date >= "2020-09-01") %>% #use this data for October
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -series_name, -contains("rolling"))),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar0")  %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date >= "2020-09-01") %>%
    pull(series_value),
  #force_row_wise = TRUE,
  num_leaves =50, # this is importnat too
  max_depth = 7,  
  learning_rate = 0.1, 
  nrounds = 222,#34,  
  min_data_in_leaf = 100, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,  
  verbose = -1)


# Remove objects
#rm(list = ls())
lgbm_mod_s1_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar1") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar1")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L,  
  max_depth = 11, 
  learning_rate = 0.1,  
  nrounds = 140,#22L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 300,  
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s2_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar2") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar2")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 30L,  
  max_depth = 11, 
  learning_rate = 0.1, 
  nrounds = 110,#8L,  
  min_data_in_leaf = 150, 
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,
  verbose = -1)


lgbm_mod_s3_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar3")  %>%
                     as_tibble() %>% 
                     filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
                     #filter(Date>= "2020-09-01") %>% #use this data for October/November
                     #filter(Date>="2020-08-01") %>% #use this date for sep test
                     select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar3") %>%
    filter(Date >= "2020-09-01" & Date< "2020-11-01") %>%
    #filter(Date>= "2020-09-01") %>%
    pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L,  
  max_depth = 10,  
  learning_rate = 0.1,  
  nrounds = 50,#20L,  
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  min_data_in_leaf = 50,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1,  
  verbose = -1)


lgbm_mod_s4_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar4")  %>%
                     filter( Date< "2020-11-01") %>%
                     as_tibble() %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar4")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 250L,  
  max_depth = 13,  
  learning_rate = 0.1,  
  nrounds = 170,#15L, 
  min_data_in_leaf = 50,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae", 
  num_threads = 8, 
  boosting = "gbdt", 
  lambda_l1 = 0.1, 
  verbose = -1)


lgbm_mod_s5_f1mae_hourly  <- lightgbm::lightgbm(
  data = as.matrix(solar_clean_weather_train_hourly %>% filter(series_name=="Solar5") %>%
                     as_tibble()  %>%
                     filter(Date< "2020-11-01") %>% select(-series_value, -series_name)),
  label = solar_clean_weather_train_hourly %>% filter(series_name=="Solar5")  %>%
    filter(Date< "2020-11-01") %>% pull(series_value),
  force_row_wise = TRUE,
  num_leaves = 20L, 
  max_depth = 8, 
  learning_rate = 0.1, 
  nrounds = 100,#10L,  
  min_data_in_leaf = 300,
  #feature_fraction = 0.7,
  #bagging_fraction = 0.7,
  objective = "mae",  
  num_threads = 8, 
  boosting = "gbdt",  
  lambda_l1 = 0.1,
  verbose = -1)
```

Predictions for November with hourly data is done below:
```{r}
predict_lgbm_b0_f1mae_hourly <- predict(lgbm_mod_b0_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b1_f1mae_hourly <- predict(lgbm_mod_b1_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b3_f1mae_hourly <- predict(lgbm_mod_b3_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b4_f1mae_hourly <- predict(lgbm_mod_b4_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b5_f1mae_hourly <- predict(lgbm_mod_b5_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b6_f1mae_hourly <- predict(lgbm_mod_b6_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_building))

predict_lgbm_b_f1mae_hourly <- rbind(predict_lgbm_b0_f1mae_hourly, predict_lgbm_b1_f1mae_hourly, predict_lgbm_b3_f1mae_hourly, predict_lgbm_b4_f1mae_hourly, predict_lgbm_b5_f1mae_hourly, predict_lgbm_b6_f1mae_hourly)
predict_lgbm_b_f1mae_hourly[predict_lgbm_b_f1mae_hourly<0.01]=0

# Solar forecast October
predict_lgbm_s0_f1mae_hourly <- predict(lgbm_mod_s0_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar %>% select(-contains("rolling"))))

predict_lgbm_s1_f1mae_hourly <- predict(lgbm_mod_s1_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s2_f1mae_hourly <- predict(lgbm_mod_s2_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s3_f1mae_hourly <- predict(lgbm_mod_s3_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s4_f1mae_hourly <- predict(lgbm_mod_s4_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s5_f1mae_hourly <- predict(lgbm_mod_s5_f1mae_hourly, as.matrix(Hourly_WeatherData_Feats_Nov_solar))

predict_lgbm_s_f1mae_hourly <- rbind(predict_lgbm_s0_f1mae_hourly, predict_lgbm_s1_f1mae_hourly, predict_lgbm_s2_f1mae_hourly, predict_lgbm_s3_f1mae_hourly, predict_lgbm_s4_f1mae_hourly, predict_lgbm_s5_f1mae_hourly)

#replacing small values with zero
predict_lgbm_s_f1mae_hourly[predict_lgbm_s_f1mae_hourly<0.15]=0
```


```{r}
predict_sb_h <- rbind(predict_lgbm_b_f1mae_hourly,predict_lgbm_s_f1mae_hourly)
rownames(predict_sb_h) <- c(buildings, solars)
#write.csv(predict_sb_h, "i2h-Nov.csv")
```

Final forecast used in the competition. We take the average of solar and buildings forecasts. 
```{r}
#prediction solars buildings
pre_solar_building <- (predict_sb_h + predict_sb_daily)/2
```

Plotting data to see how it performs.
```{r}
bind_rows(tsibble_data_Oct  %>% as_tibble() %>% 
    select(TimeDate,series_value,series_name),predict_sb_daily %>% t() %>% as_tibble()  %>% 
    pivot_longer(cols= c(1:12),names_to = "series_name", values_to= "series_value") %>%
    mutate(h= rep((1:2880), each=12))) %>%
    filter(series_name == "Building0") %>% pull(series_value) %>% plot.ts()
```
